Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-20 paper/structureScene.tex
Edit background section

%The same division is found in the field of auditory scene analysis, wherein the interest may either be 1) to isolate and identify precise events, \ie acoustic event detection (AED), or 2) to predict global attributes assigned to large time spans of audio, \ie acoustic scene classification (ASC).
In a closely related field, namely the analysis of the urban sound environment, a popular approach is the bag-of-frames (BOF) introduced in the field by Aucouturier et al. \cite{aucouturier2007bag}, where a scene is modeled by high-level summary statistics computed from local features.
Though, recently, the proposed implementation using Gaussian mixture models (GMMs) of mel-frequency cepstral coefficients (MFCCs) has been demonstrated to perform comparably to a direct averaging of the features for a variety of tasks \cite{lagrange:hal-01082501}.
This contrasts with the typical morphology of acoustic scenes, which we believe is a ``skeleton of events on a bed of textures'' \cite{nelken2013} where a few discrete sound events are superimposed upon a stationary acoustic background.
As those distinct and scarce events are most of the time highly relevant for the task at hand, it is arguably more beneficial to focus on characterizing these distinct events through describing the large-scale temporal evolution of auditory scenes rather than on the joint probability distribution of short-term features.

@@

The methods that performed the best all followed a similar structure, where a low-level feature representation, such as MFCCs, were calculated over short windows and fed separately to a classifier, such as an SVM, for training. During the classification stage, the recording to be classified was similarly processed into short windows represented by feature vectors which were classified individually by the classifier and the classifier output was combined over the recording through majority vote. This last step is known as late integration and allows the classifier to work on individual, shorter-scale sound events instead of trying to classify the recording as a whole. By doing this, the classifier is able to identify and exploit the distinct events that characterize the scene instead of trying to model its average structure. This is in agreement with the psychoacoustic results related to the perception of auditory scenes presented above.

>>>>

%The same division is found in the field of auditory scene analysis, wherein the interest may either be 1) to isolate and identify precise events, \ie acoustic event detection (AED), or 2) to predict global attributes assigned to large time spans of audio, \ie acoustic scene classification (ASC).
In the closely related field of urban sound environment analysis, a popular approach is the bag-of-frames (BOF) introduced in this context by Aucouturier et al. \cite{aucouturier2007bag}, where a scene is modeled by high-level summary statistics computed from local features.
Recently, the proposed implementation using Gaussian mixture models (GMMs) of mel-frequency cepstral coefficients (MFCCs) has been demonstrated to perform comparably to a direct averaging of the features for a variety of tasks \cite{lagrange:hal-01082501}.
This contrasts with the typical morphology of acoustic scenes, which we believe is a ``skeleton of events on a bed of textures'' \cite{nelken2013} where a few discrete sound events are superimposed upon a stationary acoustic background.
As those distinct and scarce events are most of the time highly relevant for the task at hand, it is arguably more beneficial to focus on characterizing these distinct events through describing the large-scale temporal evolution of auditory scenes rather than on the joint probability distribution of short-term features.

@@

The methods that performed the best all followed a similar structure, where low-level feature representations, such as MFCCs, were calculated over short windows and fed separately to a classifier, such as an SVM, for training. During the classification stage, the recording to be classified was similarly processed into short windows represented by feature vectors which were classified individually by the classifier and the classifier output was combined over the recording through majority vote. This last step is known as late integration and allows the classifier to work on individual, shorter-scale sound events instead of trying to classify the recording as a whole. By doing this, the classifier is able to identify and exploit the distinct events that characterize the scene instead of trying to model its average structure. This is in agreement with the psychoacoustic results related to the perception of auditory scenes presented above.
